\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-06-20 Manuscript/reply.tex
responded to more comments

From what distribution are we sampling athlete's reaction times from?

@@

Do we want to perform some formal statistical analysis of Allen's times? What
data do we want to use? I don't think it makes sense to use Allen's times at
lower level competitions versus sprinters at the world championships.

@@

This can be pretty easily addressed with a 1-2 sentence explanation in the
introduction.

@@

Table 2 is the table with the parameters from the models.  This can be moved to
the appendix? We pretty explicity define all the terms in the methods section.

>>>>

We have included other sprinting events in our analysis.

@@

Unfortunately data such as this is not easy to come by.  We found as much as we
could online, but there is simply not enough data to justify a formal analysis
of his reaction times across lower level meets.

@@

We added additional explanations to address this in the introductions section.

@@

The nomenclature for the greek variables in Table 2 are defined in the GLMM
subsection of the methods section (3.2)
